No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}

### 2013-02-05 2012-aqs/draft-aqs.tex
Added standard star chemisty and standard star observations

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% - Add standard stars to observations table
% - Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainties analysis
% [DONE] Equivalent widths significant figures.
% - Strontium
% - Carbon
% - Distance calculations revision with B-V (if available) instead of (J-K)
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot w.r.t Zolotov simulations
% - Minor merger text
% - Conclusions

% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Jacobson, Yu, Freeman

\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.  Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc. However, we find no evidence that the stream is a result of a disrupted cluster. Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex. No inverse Na-O correlation is present, and we find a positive Mg-Al relationship. Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai. Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.

@@

\keywords{Galaxy: halo, structure --- Individual: Aquarius Stream --- Stars: FGK-giants}

@@

% Consider adding a final sentence about the amount of work that has gone into stellar streaams

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2002}).

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD 44007		& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 1.033	& \dots & \dots & \dots & --185.9	& 162.9 & 0.6 \\
HD 136316		& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 1.118	& \dots & \dots & \dots & 61.0		& --37.6 & 0.4 \\
HD 141531		& 15:49:16.9 & \phn\.09:36:42.5		& 2011-03-14	& 1.309	& \dots & \dots & 350	 & 17.7		& 2.8	& 0.1 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\

\\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1

@@

% Hd 141431		: -0.96, -1.03 +/- 0.78 (MEK)

% V corrections (already applied the first number of each row)
% J221821     	:   0.30, 0.25 +/- 1.25 (MEK has -154.1, wdb ) -- diff: 5.4  (positive == higher)
% C2225316		:	0.43, 0.42 +/- 1.13 (MEK has -155.7) -- diff: -0.4 (hers is lower)
% C2306265		: 	1.14, 1.19 +/- 1.16 (MEK has -221.8) -- diff: -0.7 (hers is lower)
% J223504		:	-1.87, -1.89 +/- 1.45 (MEK has -166.9) -- diff: 2.8 (positive == higher)
% J223811		:	1.69, 1.61	+/- 1.47 (MEK has --230.1) -- diff 5.6 (positive == higher)

@@

With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}). Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile. Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths. The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD 41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is $\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.

@@

\subsection{Model Atmospheres}
We have employed the ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003}. These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere. The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe]. We interpolated the temperature, gas and radiative pressure, electron density and opacities between atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}. Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [X/H]. If unaccounted for, interpolating using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths. We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects. During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] values were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$ and logarithmically in all other parameters.

\begin{deluxetable*}{lcccccccccccccc}[h!]
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
	\colhead{Designation} &
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} & 
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} &
	\colhead{Source} \\
	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
}
\startdata
\multicolumn{10}{c}{Standard Stars} \\
\cline{1-10} \\
HD41667			& 4630	& 1.70	& 1.66 	& --1.21
				& 4605	& 1.88	& 1.44	& --1.16
				& \citet{gratton;et-al_2000} \\
HD44007			& 4790	& 1.78	& 1.63	& --1.80
				& 4850	& 2.00 	& 2.20	& --1.71
				& \citet{fulbright_2000} \\
HD142948		& 4950	& 2.19	& 1.78	& --0.79
				& 4713 	& 2.17 	& 1.38	& --0.77
				& \citet{gratton;et-al_2000} \\
\\

\multicolumn{10}{c}{Program Stars} \\
\cline{1-10} \\
C2225316-14437	& 4325				& 1.26				& 1.78				& --1.26	
				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& --1.20 $\pm$ 0.14 
				& \citet{wylie-de-boer;et-al_2012} \\
C2306265-085103	& 4170	& 0.85	& 1.81 	& --1.17
				& \dots	& \dots	& \dots	& \dots
				& \dots \\	
J221821-183424	& 4590				& 0.90				& 1.91				& --1.61
				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& --1.15 $\pm$ 0.21
				& \citet{wylie-de-boer;et-al_2012} \\
J223504-152834	& 4590				& 2.15 				& 1.45				& --0.68
				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& --0.98 $\pm$ 0.17
				& \citet{wylie-de-boer;et-al_2012} \\
J223811-104126	& 5140				& 2.96				& 1.33				& --1.45
				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& --1.20 $\pm$ 0.20
				& \citet{wylie-de-boer;et-al_2012} 
\enddata

@@

>>>>

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% [DONE] Add standard stars to observations table
% [DONE] Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainty analysis
% [DONE] Equivalent widths significant figures.
% - Strontium
% - Carbon
% - Distance calculations revision with B-V (if available) instead of (J-K)
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot w.r.t Zolotov simulations
% - Minor merger text
% - Conclusions
% - References

\author{Andrew R. Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Ken Freeman\altaffilmark{2}}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.  Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc. However, we find no evidence that the stream is a result of a classical disrupted globular cluster. Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex. No inverse Na-O correlation is present, and we find a positive Mg-Al relationship. Chemically, the group is indistinguishable from the Milky Way thick disk/halo with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai. Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.

@@

\keywords{Galaxy: halo, structure}

@@

% Consider adding a final sentence about the amount of work that has gone into stellar streaams
Wide-field surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2002}).

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 313.6		& 297.1 	& 0.1 \\
HD 44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & $-$187.0	& 161.8 	& 0.1 \\
HD 76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & $-$132.6	& 117.8		& 0.1 \\
HD 136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & \dots 	& 400 & 59.8		& $-$38.8 	& 0.1 \\
HD 141531		& 15:49:16.9 & \phn\.09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & \dots	& 350 & 17.7		& 2.8		& 0.1 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & \dots 	& 320 & 5.3			& 29.9 		& 0.1 \\

\\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.8	& 650 & 135	& $-$168.6	& $-$156.4 & 0.1 \\
C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096	& 1.0	& 650 & 100	& $-$240.4	& $-$221.1 & 0.1 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.9 	& 650 & 115	& $-$170.2	& $-$159.5 & 0.1 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& 1.0 	& 650 & 130	& $-$179.0	& $-$169.7 & 0.1 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& 1.2 	& 650 & 115	& $-$250.1	& $-$235.7 & 0.1

@@

% V corrections (already applied the first number of each row)
% HD 41667		: -0.77, -0.79 +/- 0.79
% HD 44007		: -1.12, -1.12 +/- 0.96
% HD 136316		: -1.17, -1.25 +/- 0.86
% HD 141531		: -0.96, -1.03 +/- 0.78
% HD 142948		: -1.49, -1.49 +/- 0.75
% J221821     	:   0.30, 0.25 +/- 1.25 (MEK has -154.1, wdb ) -- diff: 5.4  (positive == higher)
% C2225316		:	0.43, 0.42 +/- 1.13 (MEK has -155.7) -- diff: -0.4 (hers is lower)
% C2306265		: 	1.14, 1.19 +/- 1.16 (MEK has -221.8) -- diff: -0.7 (hers is lower)
% J223504		:	-1.87, -1.89 +/- 1.45 (MEK has -166.9) -- diff: 2.8 (positive == higher)
% J223811		:	1.69, 1.61	+/- 1.47 (MEK has --230.1) -- diff 5.6 (positive == higher)

@@

With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}). Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile. Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths. The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD 41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.6 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is $\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.

@@

\subsection{Model Atmospheres}
We have employed the ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003}. These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere. The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe]. We interpolated the temperature, gas and radiative pressure, electron density and opacities between atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}. Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [X/H]. If unaccounted for, interpolating using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths. We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects. During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] values were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$, $\log{g}$ and logarithmically in abundance ratios.

\begin{deluxetable*}{lcccccccccccccc}[h!]
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
	\colhead{Designation} &
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} & 
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} &
	\colhead{Source} \\
	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
}
\startdata
\multicolumn{10}{c}{Standard Stars} \\
\cline{1-10} \\
HD 41667		& 4630	& 1.70	& 1.66 	& $-$1.21
				& 4605	& 1.88	& 1.44	& $-$1.16
				& \citet{gratton;et-al_2000} \\
HD 44007		& 4790	& 1.78	& 1.63	& $-$1.80
				& 4850	& 2.00 	& 2.20	& $-$1.71
				& \citet{fulbright_2000} \\

HD 76932		& 5755 & 3.85 & 1.41 & $-$1.06
				\\

HD 136316		& 4350 & 0.65 & 1.83 & $-$1.92 \\

HD 141531		& 4295 & 0.60 & 1.86 & $-$1.74 \\

HD 142948		& 4950	& 2.19	& 1.78	& $-$0.79
				& 4713 	& 2.17 	& 1.38	& $-$0.77
				& \citet{gratton;et-al_2000} \\
\\

\multicolumn{10}{c}{Program Stars} \\
\cline{1-10} \\
C2225316-14437	& 4325				& 1.26				& 1.78				& $-$1.26	
				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.14 
				& \citet{wylie-de-boer;et-al_2012} \\
C2306265-085103	& 4170	& 0.85	& 1.81 	& $-$1.17
				& \dots	& \dots	& \dots	& \dots
				& \dots \\	
J221821-183424	& 4590				& 0.90				& 1.91				& $-$1.61
				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& $-$1.15 $\pm$ 0.21
				& \citet{wylie-de-boer;et-al_2012} \\
J223504-152834	& 4590				& 2.15 				& 1.45				& $-$0.68
				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& $-$0.98 $\pm$ 0.17
				& \citet{wylie-de-boer;et-al_2012} \\
J223811-104126	& 5140				& 2.96				& 1.33				& $-$1.45
				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.20
				& \citet{wylie-de-boer;et-al_2012} 
\enddata

@@

\begin{deluxetable*}{lccccccclcccccc}
\tablecolumns{15}
\tablecaption{Standard Star Abundances\label{tab:standard-star-abundances}}
\tablehead{
\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ &&
\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ 
}
\startdata
\\
 \multicolumn{7}{c}{HD 41667} & \colhead{} & \multicolumn{7}{c}{HD 44007} \\
 \cline{1-7} \cline{9-15} \\

   O \textsc{i} &   2 &    7.93 &    0.05 & $-$0.76 &    0.45 &    0.04 &&
   O \textsc{i} &   1 &    7.39 &    0.00 & $-$1.30 &    0.50 &    0.00 \\
  Na \textsc{i} &   3 &    4.87 &    0.16 & $-$1.37 & $-$0.16 &    0.09 &&
  Na \textsc{i} &   2 &    4.42 &    0.08 & $-$1.83 & $-$0.03 &    0.06 \\
  Mg \textsc{i} &   4 &    6.74 &    0.11 & $-$0.86 &    0.35 &    0.05 &&
  Mg \textsc{i} &   2 &    6.27 &    0.06 & $-$1.33 &    0.47 &    0.04 \\
  Al \textsc{i} &   4 &    5.12 &    0.11 & $-$1.33 & $-$0.12 &    0.06 &&
  Al \textsc{i} &   1 &    4.76 &    0.00 & $-$1.69 &    0.11 &    0.00 \\
  Si \textsc{i} &   5 &    6.52 &    0.05 & $-$0.99 &    0.22 &    0.02 &&
  Si \textsc{i} &   5 &    6.06 &    0.07 & $-$1.45 &    0.35 &    0.03 \\
  Ca \textsc{i} &   4 &    5.46 &    0.06 & $-$0.88 &    0.33 &    0.03 &&
  Ca \textsc{i} &   4 &    4.92 &    0.02 & $-$1.42 &    0.38 &    0.01 \\
 Sc \textsc{ii} &   6 &    2.12 &    0.13 & $-$1.03 &    0.18 &    0.05 &&
 Sc \textsc{ii} &   6 &    1.38 &    0.10 & $-$1.77 &    0.02 &    0.04 \\
  Ti \textsc{i} &   4 &    3.96 &    0.04 & $-$1.00 &    0.21 &    0.02 &&
  Ti \textsc{i} &   1 &    3.46 &    0.00 & $-$1.49 &    0.31 &    0.00 \\
 Ti \textsc{ii} &   3 &    4.12 &    0.25 & $-$0.83 &    0.38 &    0.14 &&
 Ti \textsc{ii} &   4 &    3.52 &    0.15 & $-$1.43 &    0.37 &    0.07 \\
   V \textsc{i} &   6 &    2.88 &    0.13 & $-$1.05 &    0.16 &    0.05 &&
   V \textsc{i} &   4 &    2.16 &    0.03 & $-$1.77 &    0.03 &    0.01 \\
  Cr \textsc{i} &  10 &    4.25 &    0.09 & $-$1.38 & $-$0.17 &    0.03 &&
  Cr \textsc{i} &  15 &    3.64 &    0.07 & $-$2.00 & $-$0.20 &    0.02 \\
 Cr \textsc{ii} &   3 &    4.54 &    0.25 & $-$1.10 &    0.11 &    0.14 &&
 Cr \textsc{ii} &   3 &    3.97 &    0.02 & $-$1.67 &    0.13 &    0.01 \\
  Mn \textsc{i} &   3 &    3.94 &    0.01 & $-$1.49 & $-$0.28 &    0.01 &&
  Mn \textsc{i} &   3 &    3.11 &    0.04 & $-$2.32 & $-$0.52 &    0.02 \\
  Fe \textsc{i} &  61 &    6.29 &    0.12 & $-$1.21 &    0.00 &    0.01 &&
  Fe \textsc{i} &  51 &    5.70 &    0.13 & $-$1.80 &    0.00 &    0.02 \\
 Fe \textsc{ii} &  13 &    6.28 &    0.06 & $-$1.22 & $-$0.01 &    0.02 &&
 Fe \textsc{ii} &  15 &    5.70 &    0.10 & $-$1.80 &    0.00 &    0.02 \\
  Co \textsc{i} &   3 &    3.75 &    0.11 & $-$1.24 & $-$0.03 &    0.06 &&
  Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
  Ni \textsc{i} &   7 &    4.95 &    0.12 & $-$1.27 & $-$0.06 &    0.04 &&
  Ni \textsc{i} &   4 &    4.43 &    0.04 & $-$1.79 &    0.01 &    0.02 \\
  Cu \textsc{i} &   1 &    2.76 &    0.00 & $-$1.43 & $-$0.22 &    0.00 &&
  Cu \textsc{i} &   1 &    1.84 &    0.00 & $-$2.35 & $-$0.55 &    0.00 \\
  Zn \textsc{i} &   2 &    3.33 &    0.08 & $-$1.22 & $-$0.01 &    0.06 &&
  Zn \textsc{i} &   2 &    2.83 &    0.05 & $-$1.73 &    0.07 &    0.04 \\
 Ba \textsc{ii} &   2 &    1.08 &    0.05 & $-$1.10 &    0.10 &    0.03 &&
 Ba \textsc{ii} &   2 &    0.33 &    0.05 & $-$1.85 & $-$0.05 &    0.04 \\

\cline{1-7} \cline{9-15} \\
\\
\multicolumn{7}{c}{HD 76932} && \multicolumn{7}{c}{HD 136316} \\
\cline{1-7} \cline{9-15} \\

   O \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
   O \textsc{i} &   1 &    7.20 &    0.00 & $-$1.49 &    0.43 &    0.00 \\
  Na \textsc{i} &   3 &    5.33 &    0.04 & $-$0.91 &    0.15 &    0.02 &&
  Na \textsc{i} &   2 &    4.15 &    0.03 & $-$2.09 & $-$0.17 &    0.02 \\
  Mg \textsc{i} &   3 &    7.05 &    0.20 & $-$0.55 &    0.51 &    0.12 &&
  Mg \textsc{i} &   2 &    6.05 &    0.25 & $-$1.54 &    0.38 &    0.17 \\
  Al \textsc{i} &   4 &    5.44 &    0.06 & $-$1.01 &    0.04 &    0.03 &&
  Al \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
  Si \textsc{i} &   5 &    6.74 &    0.05 & $-$0.77 &    0.29 &    0.02 &&
  Si \textsc{i} &   4 &    5.86 &    0.05 & $-$1.65 &    0.27 &    0.03 \\
  Ca \textsc{i} &   4 &    5.57 &    0.02 & $-$0.77 &    0.29 &    0.01 &&
  Ca \textsc{i} &   4 &    4.69 &    0.02 & $-$1.65 &    0.27 &    0.01 \\
  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
 Sc \textsc{ii} &   6 &    2.23 &    0.11 & $-$0.92 &    0.14 &    0.04 &&
 Sc \textsc{ii} &   5 &    1.32 &    0.05 & $-$1.83 &    0.09 &    0.02 \\
  Ti \textsc{i} &   1 &    4.35 &    0.00 & $-$0.60 &    0.46 &    0.00 &&
  Ti \textsc{i} &   3 &    3.23 &    0.03 & $-$1.72 &    0.20 &    0.02 \\
 Ti \textsc{ii} &   3 &    4.34 &    0.03 & $-$0.61 &    0.45 &    0.02 &&
 Ti \textsc{ii} &   4 &    3.52 &    0.14 & $-$1.43 &    0.49 &    0.07 \\
   V \textsc{i} &   3 &    3.15 &    0.13 & $-$0.78 &    0.28 &    0.08 &&
   V \textsc{i} &   5 &    1.88 &    0.06 & $-$2.05 & $-$0.13 &    0.03 \\
  Cr \textsc{i} &  15 &    4.44 &    0.06 & $-$1.20 & $-$0.14 &    0.01 &&
  Cr \textsc{i} &  12 &    3.52 &    0.05 & $-$2.12 & $-$0.20 &    0.02 \\
 Cr \textsc{ii} &   3 &    4.75 &    0.03 & $-$0.89 &    0.17 &    0.02 &&
 Cr \textsc{ii} &   2 &    3.83 &    0.01 & $-$1.81 &    0.11 &    0.00 \\
  Mn \textsc{i} &   3 &    4.06 &    0.03 & $-$1.37 & $-$0.31 &    0.02 &&
  Mn \textsc{i} &   3 &    3.09 &    0.02 & $-$2.34 & $-$0.42 &    0.01 \\
  Fe \textsc{i} &  51 &    6.44 &    0.10 & $-$1.06 &    0.00 &    0.01 &&
  Fe \textsc{i} &  62 &    5.58 &    0.11 & $-$1.92 &    0.00 &    0.01 \\
 Fe \textsc{ii} &  13 &    6.45 &    0.07 & $-$1.05 &    0.01 &    0.02 &&
 Fe \textsc{ii} &  14 &    5.58 &    0.12 & $-$1.92 &    0.00 &    0.03 \\
  Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
  Co \textsc{i} &   3 &    3.15 &    0.06 & $-$1.84 &    0.08 &    0.03 \\
  Ni \textsc{i} &   5 &    5.27 &    0.02 & $-$0.95 &    0.11 &    0.01 &&
  Ni \textsc{i} &   5 &    4.23 &    0.10 & $-$1.99 & $-$0.07 &    0.04 \\
  Cu \textsc{i} &   1 &    2.84 &    0.00 & $-$1.35 & $-$0.29 &    0.00 &&
  Cu \textsc{i} &   1 &    1.75 &    0.00 & $-$2.44 & $-$0.52 &    0.00 \\
  Zn \textsc{i} &   2 &    3.58 &    0.04 & $-$0.97 &    0.08 &    0.02 &&
  Zn \textsc{i} &   2 &    2.69 &    0.04 & $-$1.87 &    0.05 &    0.02 \\
 Ba \textsc{ii} &   1 &    1.16 &    0.00 & $-$1.02 &    0.04 &    0.00 &&
 Ba \textsc{ii} &   1 &    0.29 &    0.00 & $-$1.89 &    0.03 &    0.00 \\

\cline{1-7} \cline{9-15} \\
\\
\multicolumn{7}{c}{HD 141531} && \multicolumn{7}{c}{HD 142948} \\
\cline{1-7} \cline{9-15} \\
